\documentclass{report}

\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{datetime}
\usepackage{pgfgantt}
\usepackage{url}
\usepackage{hyperref}

\newdateformat{required}{\twodigit{\THEMONTH}/\twodigit{\THEDAY}/\THEYEAR}

\begin{document}

\begin{titlepage}
    \begin{center}
        \begin{huge}
        House in Your Head \\[1cm]
        Team G1-FrigidWaters \\[2.2cm]
        { \bfseries Launch Report } \\[1cm]
        Cycle \# 2\\[2.2cm]
        Date: \required\today\\[1cm]
        \end{huge}
    \end{center}
    \null \vfill
    \begin{large}
        Team Members: \\[0.5cm]
        Name: Samuel Bever\\[0.5cm]
        Name: Michael Conway\\[0.5cm]
        Name: Joseph Muoio\\[0.5cm]
        Name: Kyle Patron\\[0.5cm]
        Name: Kevin Zakszewski
    \end{large}
\end{titlepage}

\section*{\centering The System/Product}

\subsection*{System/Product Name}

House in Your Head

\subsection*{Introduction}

Amyotrophic lateral sclerosis (ALS) (also called ``Lou Gehrig's Disease'') is
a neurodegenerative disease affecting the brain and spinal cord. The motor
neurons progressively degenerate and die off, leading to the loss of muscle
control and death. Affected indivuals suffer a spectrum of symptoms
culminating in total lock-in. In this state, the patient is aware but cannot
move their body in any way. They cannot breathe on their own or even blink
their eyes. Because of this, late-stage ALS patients are unable to interface
with conventional assistive technologies. \cite{ALSsource}

The goal of the project is to build a system which people afflicted with ALS
can use to interact with their houses through Home Automation Systems (HAS).
This includes controlling the thermostat, lights, stereo, and television as
well as interfacing with social media. By having a Brain Computer Interface
(BCI) to their automated house, individuals with ALS can still interact with
their environment despite full paralysis.

% TODO
% * Project name
% * What they did
% * Limitations
This project builds off a previous senior design project. The old project had a few limitations in the design of the interface. It was a scrolling list that did not work very well. It clunky and hard to use. The interface was also too flashy which can break the concentration of the user. In addition to limitations in the interface and usability, calibration was a time consuming process and the results were not able to be saved. To overcome these problems, a new method to read the brainwaves will be used and a new interface will be tested. 

\subsection*{Highlighted Features}

\begin{itemize}
\item Calibration for individual users
\item Intuitive interface with simple selections
\item Allow users with ALS to perform basic household tasks, such as
    \begin{itemize}
        \item Turning lights on and off
        \item Adjusting the thermostat
        \item Controlling the television
    \end{itemize}
\end{itemize}

\subsection*{Sponsor or Proxy User}

Our outside stakeholder is \textbf{Sara Feldman}, PT, DPT, ATP, MDA/ALS Center
of Hope, Drexel University College of Medicine. We will be meeting with Dr.
Feldman on an ongoing basis to continually reevaluate the progress and
project goals to ensure that this product will be useful to ALS patients.

\subsection*{Issues}

Brains are complicated, and so expecting them to perform a task in a
deterministic way is not necessarily realistic. This means that we will have
to have a sophisticated signal processing system in place. There is no one
correct way to do this, and since the current method is not robust enough
for general use, we predict that this will occupy a significant portion of
the project development cycle.

% FIXME Is this too colloquial?
% FIXME Need confirmation for the other claims here -- esp "fastest"
To get an idea of the complexities involved, consider the current
best-performing text-entry interface using the Emotiv device, which requires
the user to focus on the chosen letter on the screen and observes the
involuntary recognition response when this letter flashes. Even this method
takes a long time to reliably select the correct letter, resulting in a speed
of only about 1 letter every 30 seconds. It is also mentally taxing for the
user. \cite{textentry}

% FIXME This paragraph looks a little out of place in the Issues section
%Our proposed method will take a more direct approach, where patients choose
%to divide a set of letters in half until they eventually reach their desired
%choice. At most six divisions will be necessary to select a symbol from 64
%options (allowing for all English letters, the digits 0 through 9, and a few
%other customizable entries). This means that if each choice takes less than
%five seconds, this method will be faster than the current competition.
Our proposed method will build off of the work done in the video cited
above, but our own symbols for lights, television, and thermostat will be
used in place of letters and numbers. This will allow the user to select the
appropriate action simply by concentrating on it. The method used has
already been proven to be effective and can be expanded to include any
number of options. The primary advantage to specializing our system this way
is that there will be fewer options available, which means that choices can
be accurately made much more quickly. In addition, each option is more
expressive than a single letter, allowing ideas to be communicated much more
quickly.

Gathering project requirements will present difficulties because we cannot
easily identify with the daily experiences of ALS patients and communicating
directly with late-stage ALS patients is challenging. To circumvent this, we
will have to depend heavily on our contacts at Drexel Medicine, who work
with ALS patients.

\subsection*{Project Costs}
The Emotiv device\cite{Emotiv} costs between \$300 and \$500. This cost is
being covered by the Drexel College of Engineering and College of Medicine.
Before being able to be used, the device will have to be trained, costing the
user time. The software will be fully open source, so it will be free for
users to download and use as long as they have an Emotiv device.

\subsection*{Benefits}
The biggest benefit will be the quality of life improvement for patients who
are suffering from ALS, specifically, those that are totally paralyzed and
cannot even move their eyes. The device we are developing software for is
much cheaper than the alternatives, which can cost upwards of \$17,000.
Since this project is open source, there is a large potential for our
project to grow and be used in future work.

\newpage
\section*{\centering The Team}

\subsection*{Team Name}

G1-FrigidWaters

\subsection*{Team Members and Their Specialties}

Samuel Bever enjoys working in algorithms, artificial intelligence, and
graphics. Role: Tester.

Michael Conway has experience and interests in the areas of algorithms,
programming languages and computer security. Role: Technical Lead.

Joseph Muoio has experience and interests in the areas of AI, mobile app
development and software development. Role: Team Leader.

Kyle Patron is interested in mathematics, particularly as it relates to
signal processing and machine control. Role: Tools lead.

Kevin Zakszewski has experience in UI/UX design and front end
implementation. Role: Lead Designer.

\subsection*{Team Communication}

Our team will be meeting at least once a week on Wednesdays at 5pm to discuss
our progress, outline our tasks for that week, and address any other issues.
If necessary, more meetings will be scheduled for the remainder of that
week. Most group communication outside of these meetings will be done via
email. For source code management, we will be using a GitHub \cite{github} repository,
which comes with an issue tracker and a project wiki. We will also be using
Review Board in order to organize and distribute code reviews to the team.
% FIXME Cite Review Board, or at least capitalize it (I hadn't heard of it).
% Maybe cite GitHub too.

\subsection*{Team Issues}

We are all busy and have many other school and work commitments. Finding
time to meet on a regular basis will be important but possibly difficult.

There are some differences of opinion when it comes to technical aspects of
this project. We are still debating which language we should use.

\newpage
\section*{\centering The Plan}

\subsection*{Objectives}

Our goals for this cycle are to

\begin{itemize}
    \item Revise our requirements and design specifications based on
        information from the previous cycle
    \item Develop a test plan
    \item Develop the Emotiv-based UI, which is the core of the project
    \item Refine and extend the HAS interface begun in the previous cycle
    \item Integrate these two components into a single package that provides
        the basic functionality of the end product
        % TODO more of these?
\end{itemize}

\subsection*{Schedule}

\begin{tabular}{| l | l | l |}
    \hline
    Week & Person & Contribution \\
    \hline \hline

    1 & Everyone & Revise and update launch report for C2 \\ \hline
    1-3 & & Revise requirements \\ \hline
    2-5 & Sam Bever & Develop test plan \\ \hline
    3-6 & & Revise system design \\ \hline
    1-3 & Kyle Patron & Experiment with Emotiv functionality \\ \hline
    3-6 & Kyle Patron, Kevin Zakszewski & Develop Emotiv-based UI \\ \hline
    3-6 & Michael Conway & Refine and extend HAS interface \\ \hline
    7-8 & Sam Bever & Integrate and test C2 implementation \\ \hline
    7-9 & Everyone & Revise and update launch report for C3 \\ \hline
    8-11 & Joe Muoio, Sam Bever & Prepare presentation \\ \hline

\end{tabular}

\begin{ganttchart}{1}{11}
    \gantttitle{Winter Term}{11} \\
    \gantttitlelist{1,...,11}{1} \\

    % These are all "during or at the end of week #"
    \ganttbar{Revise and update launch report for C2}{1}{1} \\
    \ganttlinkedmilestone{Launch Report C2}{1} \\
    \ganttbar{Revise requirements}{1}{3} \\
    \ganttlinkedmilestone{SRS C2}{3} \\
    \ganttbar{Develop test plan}{2}{5} \\
    \ganttlinkedmilestone{Test Specification C2}{5} \\
    \ganttbar{Revise system design}{3}{6} \\
    \ganttlinkedmilestone{SDS C2}{6} \\
    \ganttbar{Experiment with Emotiv functionality}{1}{3} \\
    \ganttbar{Develop Emotiv-based UI}{3}{6} \\
    \ganttbar{Refine and extend HAS interface}{3}{6} \\
    \ganttbar{Integrate and test C2 implementation}{7}{8} \\
    \ganttlinkedmilestone{Implementation C2}{8} \\
    \ganttbar{Revise and update launch report for C3}{7}{9} \\
    \ganttlinkedmilestone{Launch Report C3}{9} \\
    \ganttbar{Prepare presentation}{8}{11} \\
    \ganttlinkedmilestone{Presentation C2}{11}

    \ganttlink{elem8}{elem9}
    \ganttlink{elem9}{elem11}
    \ganttlink{elem10}{elem11}

\end{ganttchart}

\newpage
\section*{\centering Table of Contributions}
\begin{tabular}{| l | l | l | l |}
    \hline
     & Section & Writing & Editing \\
    \hline \hline
    1 & Project & Joe Muoio  & Mike Conway \\ \hline
    2 & Team & Everyone & Sam Bever \\ \hline
    3 & Plan & Kyle Patron & Kevin Zakszewski \\ \hline
\end{tabular}

\newpage
\begin{thebibliography}{1}

    \bibitem{ALSsource} The ALS Association. (2014, October, 5). \textit{What
        is ALS?} [Online]. Available:
        \url{http://www.alsa.org/about-als/what-is-als.html}
 
    \bibitem{Emotiv} Emotiv, Inc. (2014, October, 6). \textit{Emotiv|EEG
        System} [Online]. Available: \url{http://emotiv.com/}

        % FIXME
    \bibitem{textentry} http://youtu.be/08GNE6OdNcs

    \bibitem{github} GitHub (2015, February, 7). \textit{GitHub} [Online]. Available: \url{https://github.com/about}


\end{thebibliography}

\newpage
\noindent I certify that:
\begin{itemize}
\item This paper/project/exam is entirely my own work.
\item I have not quoted the words of any other person from a printed source or a website without indicating what has been quoted and providing an appropriate citation.
\item I have not submitted this paper / project to satisfy the requirements of any other course.
\end{itemize}

\vspace{1cm}
\noindent\makebox[\textwidth][l]{
Signature:
\makebox[5cm][l] {\underline{Samuel Bever}} 
\ \ Date:
\makebox[4cm][l] {\underline{\required\today}} 
}


\vspace{0.5cm}
\noindent\makebox[\textwidth][l]{
Signature:
\makebox[5cm][l] {\underline{Michael Conway}} 
\ \ Date:
\makebox[4cm][l] {\underline{\required\today}} 
}

\vspace{0.5cm}
\noindent\makebox[\textwidth][l]{
Signature:
\makebox[5cm][l] {\underline{Joe Muoio}} 
\ \ Date:
\makebox[4cm][l] {\underline{\required\today}} 
}

\vspace{0.5cm}
\noindent\makebox[\textwidth][l]{
Signature:
\makebox[5cm][l] {\underline{Kyle Patron}} 
\ \ Date:
\makebox[4cm][l] {\underline{\required\today}} 
}

\vspace{0.5cm}
\noindent\makebox[\textwidth][l]{
Signature:
\makebox[5cm][l] {\underline{Kevin Zakszewski}} 
\ \ Date:
\makebox[4cm][l] {\underline{\required\today}} 
}

\vspace{\fill}
\subsection*{Grading}
The grade is given on the basis of quality, clarity, presentation, completeness, and writing of each section in the report. This is the grade of the group. Individual grades will be assigned at the end of the term when peer reviews are collected.
\end{document}
